The Impact of Anthropogenic Forcing on ENSO Amplitude

### 2021-12-15 presentations/presentation/presentation.tex
wooohooooo here goes

\begin{frame}{Climate Change and Variability}
  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item Global warming
    \item Long-term trends vs short-term randomness
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{intro_fig_3.pdf}{Global mean land air temperature in GISSTEMP 4 dataset. \citep{gistemp2019giss} and \citep{lenssen2019improvements}}{this}
  \end{columns}
\end{frame}

@@

\begin{frame}{Methods Overview}
  \begin{itemize}
  \item Precollected predictions of sea surface temperature from climate models.
  \item Calculate ENSO intensity in model output.
  \item Use single forcing ensembles to estimate contributions each forcing item.
  \item Plot correlation between ENSO intensity and ocean temperature to examine relationship between heat transfer, forcing, and ENSO.
  \item Use wavelet analysis to analyze changes to ENSO at different frequencies.
  \end{itemize}
\end{frame}

\begin{frame}{Role of Mentor and Student}
  \begin{columns}[t]
    \column{.5\textwidth}
    Student:
    \begin{itemize}
    \item Analyze raw data on computer
    \item Produce graphics for analysis and publication
    \item Write documentation
    \item Identify key features of results
    \end{itemize}
    \column{.5\textwidth}
    Mentor:
    \begin{itemize}
    \item Review student writing
    \item Interpret results in the context of climatology
    \item Conduct parallel analysis
    \item Provide raw data from facility
    \end{itemize}
  \end{columns}

\end{frame}

@@

\begin{frame}{ENSO is Becoming Stronger}
  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item Increase in ENSO intensity in both ensembles.
    \item Increase slows down in CESM1 and decreases in CESM2 after around 2050.
      \begin{itemize}
      \item May be caused by aerosol emissions.
      \end{itemize}
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{ff_compare.pdf}{ENSO intensity ensemble mean and standard error for CESM1 and CESM2}{ff_compare}
  \end{columns}
\end{frame}

@@

\begin{frame}{Discussion}
  \begin{itemize}
  \item Rising greenhouse gas levels increase Pacific Ocean stratification, strengthening ENSO cycle.
  \item Aerosol influence nonlinear because aerosol levels are not purely increasing.
  \item Stronger ENSO will lead to greater climate variability and extreme weather.
  \item
  \end{itemize}
\end{frame}

\begin{frame}{Conclusions and Discussion}
  \begin{itemize}
  \item There is likely to be an increase in ENSO strength over the next 100 years. Agrees with \citet{cai2018increased}.
  \item Variance increase is likely caused by the combined influence of greenhouse gasses and aerosols.
  \item Global warming increases ENSO intensity by warming upper layers of the Pacific faster than central layers.
  \end{itemize}
\end{frame}

\begin{frame}{Application, Limitation, and Next Steps}
  \begin{description}
  \item[\alert{Application}] Improve prediction ability to help people prepare for increased likelihood of extreme weather.
  \item[\alert{Limitation}] Niño 3.4 index may not be fully accurate for various models \citep{cai2018increased}. Also, CESM may contain biases and is not completely accurate.
  \item[\alert{Next steps}] Examine other variables to further analyze mediator process, continue wavelet analysis methods to focus on individual frequency bands.
  \end{description}
\end{frame}

>>>>

\begin{frame}{Climate Change and Variability}
  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item Global warming
    \item Long-term trends vs short-term randomness
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{intro_fig_3.pdf}{Global mean land air temperature in GISSTEMP 4 dataset. \citep{gistemp2019giss} and \citep{lenssen2019improvements}}{woohoo}
  \end{columns}
\end{frame}

@@

% \begin{frame}{Methods Overview}
%   \begin{itemize}
%   \item Precollected predictions of sea surface temperature from climate models.
%   \item Calculate ENSO intensity in model output.
%   \item Use single forcing ensembles to estimate contributions each forcing item.
%   \item Plot correlation between ENSO intensity and ocean temperature to examine relationship between heat transfer, forcing, and ENSO.
%   \item Use wavelet analysis to analyze changes to ENSO at different frequencies.
%   \end{itemize}
% \end{frame}

% \begin{frame}{Role of Mentor and Student}
%   \begin{columns}[t]
%     \column{.5\textwidth}
%     Student:
%     \begin{itemize}
%     \item Analyze raw data on computer
%     \item Produce graphics for analysis and publication
%     \item Write documentation
%     \item Identify key features of results
%     \end{itemize}
%     \column{.5\textwidth}
%     Mentor:
%     \begin{itemize}
%     \item Review student writing
%     \item Interpret results in the context of climatology
%     \item Conduct parallel analysis
%     \item Provide raw data from facility
%     \end{itemize}
%   \end{columns}
% \end{frame}

@@

\begin{frame}{ENSO is Becoming Stronger}
  \begin{columns}
    \column{0.4\textwidth}
    \begin{itemize}
    \item Increase in ENSO intensity in both ensembles.
    \item Increase slows down in CESM1 and decreases in CESM2 after around 2050.
    \end{itemize}
    \column{0.6\textwidth}
    \myfig{ff_compare.pdf}{ENSO intensity ensemble mean and standard error for CESM1 and CESM2}{ff_compare}
  \end{columns}
\end{frame}

@@

\begin{frame}{Discussion}
  \begin{itemize}
  \item Rising greenhouse gas levels increase Pacific Ocean stratification, strengthening ENSO cycle.
  \item Aerosol influence is nonlinear because aerosol levels are not purely increasing.
  \item Stronger ENSO may lead to greater temperature variability and extreme weather.
  \item CESM1 and CESM2 conflict in their prediction of the changes to ENSO's frequency.
  \end{itemize}
\end{frame}

\begin{frame}{Limitations and Applications}
  Limitations:
  \begin{itemize}
  \item Niño 3.4 index shown to be inaccurate for some models \citep{cai2018increased}.
  \item CESM may contain biases.
  \end{itemize}
  Application: to improve our ability to predict ENSO and help people prepare for increased likelihood of extreme weather.
\end{frame}
% \begin{frame}{Limitations}
%   \begin{itemize}
%   \item Niño 3.4 index is inaccurate for certain models.
%   \item Only one climate model used in analysis.
%   \item Climate models are all imperfect.
%   \end{itemize}
% \end{frame}

% \begin{frame}{Future Research}
%   \begin{itemize}
%   \item Conduct similar analysis on large ensembles of other climate models.
%   \end{itemize}
% \end{frame}

% \begin{frame}{Conclusions and Discussion}
%   \begin{itemize}
%   \item There is likely to be an increase in ENSO strength over the next 100 years. Agrees with \citet{cai2018increased}.
%   \item Variance increase is likely caused by the combined influence of greenhouse gasses and aerosols.
%   \item Global warming increases ENSO intensity by warming upper layers of the Pacific faster than central layers.
%   \end{itemize}
% \end{frame}
%
% \begin{frame}{Application, Limitation, and Next Steps}
%   \begin{description}
%   \item[\alert{Application}] Improve prediction ability to help people prepare for increased likelihood of extreme weather.
%   \item[\alert{Limitation}] Niño 3.4 index may not be fully accurate for various models \citep{cai2018increased}. Also, CESM may contain biases and is not completely accurate.
%   \item[\alert{Next steps}] Examine other variables to further analyze mediator process, continue wavelet analysis methods to focus on individual frequency bands.
%   \end{description}
% \end{frame}
